Efficient pedigree recording for fast population genetics simulation

### 2018-10-12 forwards_paper.tex
tweaks for submission
Link ftprime in main readme; correct sim setup code and sims/README txt

%% for submitting with responses to reviews
\newif\ifsubmission
% \submissiontrue
\submissionfalse
\ifsubmission
    % % stuff for submission
    \usepackage[nofiglist,nomarkers,figuresonly]{endfloat}
    \usepackage{setspace}
    % \doublespacing
    \bibliographystyle{plos2015}
    \newcommand\citet{\cite}
    \newcommand\citep{\cite}
    \renewcommand\includegraphics{\relax}
    \renewcommand{\includegraphics}[2][]{\relax}
    \renewcommand{\figurename}{Fig.}
    \newcommand{\Figure}{Fig }
    \newcommand{\Figures}{Fig }
\else
    % for the nice version
    \usepackage[square,sort,comma,numbers]{natbib} \bibpunct{(}{)}{;}{author-year}{}{,} 
    \bibliographystyle{plainnat}
    \newcommand{\Figure}{{Figure }}
    \newcommand{\Figures}{{Figures }}
\fi
% grrr
\newcommand{\citetx}[2][]{\ifsubmission#1 \cite{#2}\else\citet{#2}\fi}

% Responses to reviews
\input{review-response-commands}
% set this to show line numbers and include responses to reviews or not
\newif\ifreviewresponses
\reviewresponsestrue  % include them
% \reviewresponsesfalse  % don't include them
\newcommand{\responsefile}{review-responses}  % name of the review responses file

@@

To use the methods with \simupop{}, we created a python module
(available at \url{https://github.com/ashander/ftprime})
that manages communication between the forward simulator and \tskit{}.
We implemented simulations in a Python script, usable as a command-line utility,
taking input parameters for population size $N$ and scaled recombination rate $\rho$.
As for the \fwdpp{} simulations above, we set scaled mutation rate $\theta=4N\mu=\rho$
(where $\mu$ is the per-site mutation rate multiplied by the number of sites),
and used a simplify interval of 1000 generations and simulated for $T=10N$ generations in each
simulation.
% introducing deleterious mutations at a rate of $\rho/100$ per generation.
% Because \simupop{} requires explicit locations for loci, we set the number of
% loci $n=\rho / (4Nr)$ and for these simulations without selection marked $0$ of
% these as selected loci.

>>>>

%% for submitting with responses to reviews
\newif\ifsubmission
\submissiontrue
% \submissionfalse
\ifsubmission
    % % stuff for submission
    \usepackage[nofiglist,nomarkers,figuresonly]{endfloat}
    \usepackage{setspace}
    % \doublespacing
    \bibliographystyle{plos2015}
    \newcommand\citet{\cite}
    \newcommand\citep{\cite}
    % \renewcommand\includegraphics{\relax}
    % \renewcommand{\includegraphics}[2][]{\relax}
    \renewcommand{\figurename}{Fig.}
    \newcommand{\Figure}{Fig }
    \newcommand{\Figures}{Fig }
\else
    % for the nice version
    \usepackage[square,sort,comma,numbers]{natbib} \bibpunct{(}{)}{;}{author-year}{}{,} 
    \bibliographystyle{plainnat}
    \newcommand{\Figure}{{Figure }}
    \newcommand{\Figures}{{Figures }}
\fi
% grrr
\newcommand{\citetx}[2][]{\ifsubmission#1 \cite{#2}\else\citet{#2}\fi}

% Responses to reviews
% set this to show line numbers and include responses to reviews or not
\newif\ifreviewresponses
\reviewresponsestrue  % include them
% \reviewresponsesfalse  % don't include them
\input{review-response-commands}
\newcommand{\responsefile}{review-responses}  % name of the review responses file

@@

To use the methods with \simupop{}, we created a python module
(available at \url{https://github.com/ashander/ftprime}, version 0.0.6)
that manages communication between the forward simulator and \tskit{}.
We implemented simulations in a Python script, usable as a command-line utility,
taking input parameters for population size $N$ and scaled recombination rate $\rho$.
As for the \fwdpp{} simulations above, we set scaled mutation rate $\theta=4N\mu=\rho$
(where $\mu$ is the per-site mutation rate multiplied by the number of sites),
and used a simplify interval of 1000 generations and simulated for $T=10N$ generations in each
simulation.
% introducing deleterious mutations at a rate of $\rho/100$ per generation.
% Because \simupop{} requires explicit locations for loci, we set the number of
% loci $n=\rho / (4Nr)$ and for these simulations without selection marked $0$ of
% these as selected loci.
